On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/manuscript.tex
attempted to fix paragraphs

\jy{Are we reporting the C-P intervals? Clarify the desciption and
  cite the reference.}

@@

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where standard normal, Student's $t$, and 
recentered percentile CI $\phi$ coverage rates were greater for stronger 
dependences 
regardless of the sign, $\rho$ coverage rates for these CIs seem to be greater 
only for 
stronger negative dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
\jy{I don't follow this. Are you talking about mu only? Even for mu,
  the statement does not look right.} \mc{for lag-1 autocorrelation}
\jy{This would invalidate our explanation using the effective sample
  size. Let's tune it down or remove it.}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

One of the goals of this study was to provide some practical recommendations for
necessary sample sizes when using block bootstrap to estimate the parameters of
serially dependent data. When using Student's $t$ intervals and the
marginal
\jy{Recall that t is not different from normal when sample size is
  large. So the recommendation is to do t always since it performs
  better for small samples.}
distribution and temporal dependence is 
unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
to estimate the standard deviation. If
\jy{Don't discuss these. The recommended method is regardless of what
  the dependence struture and marginald istribution are. That's why we
  did the study. Just gave recommendations based on both
  scenarios. Rewrite this paragraph.}
the dependence structure or the marginal distribution is already known, a 
lesser $n$ may be 
adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating the standard deviation. For negative values of $\phi$, coverage of all 
parameters is higher in general. Under a marginal standard normal distribution, 
Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$  when 
using smaller sample sizes, meaning that if $\phi$
\jy{These statements are not to the point. Let's not discuss the case
  where phi is know or not. They are not known. We want the method to
  be robust to phi and the true marginal distribution.}
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. 
Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
a marginal standard normal distribution, whereas $n \geq 1600$ may be required
under under a marginal exponential distribution. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for~$\phi$.

@@

Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of~$n$.

The results for $\sigma_x$ with $l = \lceil 2n^{1/3} \rceil$ look very similar 
to 
those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
rates of $\sigma_x$ do 
look 
slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in~$l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.

\jy{Put the small paragraphs into a bigger one.}

As shown in \textbf{Figure~\ref{fig:norm2}},
recentered percentile and standard CIs have slightly lower coverage rates when
estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
Although it is still a problem, the coverage deterioration appears to be less 
dramatic for BCA,
BC, and percentile CIs.

Aside from these differences, the overall changes
in performance when other experimental factors are changed are the same as
when $l = \lceil n^{1/3} \rceil$.

>>>>

\jy{Are we reporting the C-P intervals? Clarify the desciption and
  cite the reference.}
\mc{addressed}

@@

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where standard normal, Student's $t$, and 
recentered percentile CI $\phi$ coverage rates were greater for stronger 
dependences 
regardless of the sign, $\rho$ coverage rates for these CIs seem to be greater 
only for 
stronger negative dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
\jy{I don't follow this. Are you talking about mu only? Even for mu,
  the statement does not look right.} \mc{for lag-1 autocorrelation}
\jy{This would invalidate our explanation using the effective sample
  size. Let's tune it down or remove it.}
\mc{this observation was for lag-1 autocorrelation. does it still invalidate 
our effective sample size explanation?}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

One of the goals of this study was to provide some practical recommendations for
necessary sample sizes when using block bootstrap to estimate the parameters of
serially dependent data. When using Student's $t$ intervals and the
marginal
\jy{Recall that t is not different from normal when sample size is
  large. So the recommendation is to do t always since it performs
  better for small samples.} \mc{addressed}
distribution and temporal dependence is 
unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
to estimate the standard deviation. Student's $t$ is always preferable to
Standard Normal CIs
as they performs better for smaller sample sizes and performs as good or better
for larger sample sizes.
\jy{Don't discuss these. The recommended method is regardless of what
  the dependence struture and marginald istribution are. That's why we
  did the study. Just gave recommendations based on both
  scenarios. Rewrite this paragraph.}
\mc{addressed}
\jy{These statements are not to the point. Let's not discuss the case
  where phi is know or not. They are not known. We want the method to
  be robust to phi and the true marginal distribution.}
\mc{addressed}
Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
a marginal standard normal distribution, whereas $n \geq 1600$ may be required
under under a marginal exponential distribution. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for~$\phi$.

@@

Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
\rceil$ look very similar 
to 
those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
rates of $\sigma_x$ do 
look 
slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in~$l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
Recentered percentile and standard CIs have slightly lower coverage rates when
estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
Although it is still a problem, the coverage deterioration appears to be less 
dramatic for BCA,
BC, and percentile CIs. Aside from these differences, the overall changes
in performance when other experimental factors are changed are the same as
when $l = \lceil n^{1/3} \rceil$.

### 2024-01-09 Manuscript/reply.tex
Reference for Clopper-Pearson
attempted to fix paragraphs

\mc{for exponential, the first-order autocorrelation coefficient
is not the same as $\phi$, should I define $\rho$ as the first-order 
autocorrelation coefficient in the manuscript so that I can use the greek letter
in the plot}
\jy{Yes.}

@@

Thank you for pointing this out. We modified the Design section to include a 
specification of the interval type for the coverage rate, as well as an 
acknowledgement of its flaw.

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}
\mc{I included it in the paper but they do not seem too different}
\jy{Point out the location of the changes in the text.}

We have also included a figure in the Results section which 
uses exact 
Clopper-Pearson CIs to verify that the choice of interval
for the binomial proportion did not cause undercoverage in this case.

>>>>

\mc{for exponential, the first-order autocorrelation coefficient
is not the same as $\phi$, should I define $\rho$ as the first-order 
autocorrelation coefficient in the manuscript so that I can use the greek letter
in the plot}
\jy{Yes.}
\mc{addressed}

@@

Thank you for pointing this out. We tried both Wald intervals and exact 
Clopper-Pearson intervals. Although we did not find a major difference between
the two, we have switched to Clopper-Pearson intervals to avoid the potential
undercoverage.

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}
\mc{I included it in the paper but they do not seem too different}
\jy{Point out the location of the changes in the text.}
\mc{addressed}

We have discussed this in the third paragraph of the Marginal Standard Normal 
Distribution subsection of the Design section, and we have provided a reference
for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
used \citep{PropCIs}.
